\documentclass{article}[12pt]

\usepackage{geometry}
\geometry{
 a4paper,
 total={210mm,297mm},
 left=16mm,
 right=16mm,
 top=16mm,
 bottom=16mm,
 }

\begin{document}

\pagestyle{empty}
\setlength{\parindent}{0cm}
\setlength{\parskip}{1em}

\begin{center} 
{\Large Informed Consent Form} 
\end{center}

{\bf STUDY TITLE: Gaze-Based Object Tracking}

\paragraph{Protocol Directors:} {\bf Raphael Sznitman $<$raphael.sznitman@epfl.ch$>$  \\
\mbox{ }\hspace{9em}Mario Christoudias $<$mario.christoudias@epfl.ch$>$}

\paragraph{DESCRIPTION:} You are invited to participate in {\bf a research study} whose focus is to study peoples' ability to visually track an object in a video sequence. The study consists of visually tracking a single object in each of three video sequences, during which we will be recording your eye gaze. The only data that we will collect are the coordinates of your gaze, {\bf no images will be collected}. The data we collect will be used for {\bf research purposes only} and will {\bf published online} to be used by the research community. {\bf Your identity will be anonymized} in all and any material gathered during this study.

\paragraph{TIME INVOLVEMENT:} The study will take 5 to 10 minutes of your time.

\paragraph{RISKS AND BENEFITS:} The risk associated with this study is {\bf non-existent}. The benefit is the development of improved human-computer interfaces particularly in the context of interactive video display.

\paragraph{SUBJECT'S RIGHTS:} If you have read this form and have decided to participate in this project, please understand your participation is voluntary and you have the right to withdraw your consent or discontinue participation at any time without penalty or loss of benefits to which you are otherwise entitled. Your individual privacy will be maintained in all published and written data resulting from the study.

{\bf CONTACT INFORMATION}: If you have questions, concerns or complaints about this research, its procedures, risks and benefits, contact either of the Protocol Directors (the people who are conducting the test).

\vspace{2em}

{\bf I give consent to be recorded during this experiment and the data gathered from my input to be processed for research purposes.} \\ \\ \\
{\bf SIGNATURE \underline{\hspace{15em}} \hspace{2em} {\bf DATE \underline{\hspace{10em}}} \\ \\ \\
{\bf NAME (in printed letters) \underline{\hspace{15em}}

\end{document}